### 2013-06-06 menger.tex
added H-closed proof

  \begin{proof}
    TODO: this
  \end{proof}

@@

  \begin{proposition}
    Every subset of a compact set is relatively compact to the entire space.
  \end{proposition}

@@

  \begin{proof}
    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$ is trivial. We may see $(b)\Rightarrow(a)$ since for regular spaces, the closure of a relatively compact set is compact.

    To prove $(c)\Rightarrow(b)$, let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable. Let $\mathfrak{C}$ be the collection of all countable covers of $X$. We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
      \begin{itemize}
        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{\<n\>}$ so that
          \[
            R_\emptyset = 
            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
          \]
        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{s\concat\<n\>}$ so that 
          \[
            R_s = 
            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
          \]
      \end{itemize}

@@

  We generalize this result for non-metric spaces.

>>>>

  \begin{proof}
    The backward implication is trivial, so let $X$ be $H$-closed. For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$. Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
  \end{proof}

@@

@@

  \begin{proof}
    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$, $(b)\Rightarrow(a)$ are trivial.

    To prove $(c)\Rightarrow(b)$, let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable. Let $\mathfrak{C}$ be the collection of all countable covers of $X$. We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
      \begin{itemize}
        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{\<n\>}$ so that
          \[
            R_\emptyset = 
            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
          \]
        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{s\concat\<n\>}$ so that 
          \[
            R_s = 
            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
          \]
      \end{itemize}

@@
